Stochastic Properties of EIP-1559 Basefees

### 2021-06-02 eip1559_MDPI/manuscript.v2.tex
update

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Analyse Gas Fee Simulations}
\label{section:gas_fees}

@@

@@

The purpose of this study was to understand under what conditions the EIP-1559 pricing mechanism would behave as a stationary process. We believe this as a critical first step to understanding the constraints to engineering a well-designed system. Given the enormity of the Ethereum project, understanding these fundamentals are needed for setting up well-designed simulation experiments to help capture all the edge cases that may arise so that the number of updates and patches are minimized prior to release.

@@

Ideally, we would like EIP-1559 to behave as a stationary process. Hence, more investigation is required to understand the setup that is necessary to achieve these conditions before proper simulation studies are implemented.

@@

%=====================================
% References, variant B: internal bibliography
%=====================================
\begin{thebibliography}{999}
% Reference 1
\bibitem[Buterin(2019)]{But19}
Buterin, V. Blockchain Resource Pricing, Apr 2019. Accessed on: May 2021. [Online]. Available: https://github.com/ethereum/research/blob/master/papers/pricing/ethpricing.pdf
% Reference 2
\bibitem[Roughgarden(2020)]{Rou20}
Roughgarden, T. Transaction Fee Mechanism Design for the Ethereum Blockchain: An Economic Analysis of EIP-1559, Dec 2020. Accessed on: Apr 2021. [Online]. Available: https://arxiv.org/abs/2012.00854
% Reference 3
\bibitem[Monnot(2021)]{Mon21}
Monnot, B. Agent-based Simulation Environment for EIP-1559, Apr 2019. Accessed on: Apr 2021. [Online]. Available: hhttps://github.com/barnabemonnot/abm1559
% Reference 4
\bibitem[Trapani(2019)]{Tra19}
Trapani, L. Testing for Strict Stationarity in a Random Coefficient Autoregressive Model, Jan 2019. Accessed on: Apr 2021. [Online]. Available: https://arxiv.org/abs/1901.01077
% Reference 5
\bibitem[Chatfield(1989)]{Cha89}
Chatfield, C. \textit{The Analysis of Time Series: An Introduction}, 4th ed.; Chapman and Hall: New York, US, 1989.
% Reference 6
\bibitem[Nicholls(1982)]{Nic82}
Nicholls, D.; Quinn, D. \textit{Random Coefficient Autoregressive Models: An Introduction};  Springer-Verlag: Berlin, Germany, 1982.
% Reference 7
\bibitem[Wang(2003)]{Wan03}
Wang, D. Coefficient Autoregressive Models. PhD Dissertation, North Carolina State University, North Carolina, 2003.
\end{thebibliography}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Analyse Gas Fees}
\label{section:gas_fees}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}
\label{section:discussion}

In Section \ref{section:gas_fees}, we analysed  the stationarity of our simulated output using the EIP-1559 system described in (\ref{eq:eip1559}) and (\ref{eq:fk}). We studied its stochastic behaviour by applying the theory behind RCA processes and  also by applying the ADF test on each of our simulations.

We made a strong assumption of $\delta_{k}$ being normal and strictly stationary which is a direct fallout of assuming users pay 21,000 gas per transaction and are Poisson distributed, as per \textit{abm1559} simulator. In a real-world setting, we see this as being one of the most rudimentary of all scenarios, where Ethereum transactions are experiencing a state of non-congestion and the expectation of usage is constant. Hence, we call this the \textit{base case assumption} and see this as a first-step to mathematically understanding this system, when investigating as a stochastic process.

A more realistic setting could involve modelling $\delta_{k}$ as a linear system to include other non-stationary terms such as trend, seasonality and other forms of idiosyncratic volatility to capture a collection of scenarios that may be modelled after the real-world. A good strategy could begin with the simple framework described here, then successively include various structural components much like is done when working with the Linear Gaussian Model described in \cite{Dur12}. Once determined, batch simulations can be run to act as stress tests to study how this system would behave under various conditions. We see this as necessary when designing a robust system to help capture various edge cases prior to deployment,  so that the number of updates and patches are minimized prior to release. However, this more challenging level of analysis involving various non-stationary assumptions for $\delta_{k}$, is the subject of future work.

@@

The purpose of this study was to understand under what conditions the EIP-1559 pricing mechanism would behave as a stationary process. We believe this as a critical first step to understanding the constraints to engineering a well-designed system. Given the enormity of the Ethereum project, understanding these fundamentals are needed for setting up well-designed simulation experiments.

@@

Ideally, we would like EIP-1559 to behave as a stationary process under the base case assumption of $\delta_{k}$ being normal and strictly stationary. Hence, more investigation is required to understand the setup that is necessary to achieve these conditions before proper simulation studies are implemented.

@@

%=====================================
% References, variant B: internal bibliography
%=====================================
\begin{thebibliography}{999}
% Reference 1
\bibitem[Buterin(2019)]{But19}
Buterin, V. Blockchain Resource Pricing, Apr 2019. Accessed on: May 2021. [Online]. Available: https://github.com/ethereum/research/blob/master/papers/pricing/ethpricing.pdf
% Reference 2
\bibitem[Roughgarden(2020)]{Rou20}
Roughgarden, T. Transaction Fee Mechanism Design for the Ethereum Blockchain: An Economic Analysis of EIP-1559, Dec 2020. Accessed on: Apr 2021. [Online]. Available: https://arxiv.org/abs/2012.00854
% Reference 3
\bibitem[Monnot(2021)]{Mon21}
Monnot, B. Agent-based Simulation Environment for EIP-1559, Apr 2019. Accessed on: Apr 2021. [Online]. Available: hhttps://github.com/barnabemonnot/abm1559
% Reference 4
\bibitem[Trapani(2019)]{Tra19}
Trapani, L. Testing for Strict Stationarity in a Random Coefficient Autoregressive Model, Jan 2019. Accessed on: Apr 2021. [Online]. Available: https://arxiv.org/abs/1901.01077
% Reference 5
\bibitem[Chatfield(1989)]{Cha89}
Chatfield, C. \textit{The Analysis of Time Series: An Introduction}, 4th ed.; Chapman and Hall: New York, US, 1989.
% Reference 6
\bibitem[Nicholls(1982)]{Nic82}
Nicholls, D.; Quinn, D. \textit{Random Coefficient Autoregressive Models: An Introduction};  Springer-Verlag: Berlin, Germany, 1982.

\bibitem[Durbin(2012)]{Dur12}
Durbin, J.; Koopman, S. \textit{Time Series Analysis by State Space Methods}, 2nd ed.;  Oxford University Press, Oxford, England, 2012.

% Reference 7
\bibitem[Wang(2003)]{Wan03}
Wang, D. Coefficient Autoregressive Models. PhD Dissertation, North Carolina State University, North Carolina, 2003.
\end{thebibliography}
